\addcontentsline{toc}{section}{References}

\begin{thebibliography}{99}
  \bibitem{mcdowell2016} McDowell Group. (2016). \textit{ Juneau Visitor Profile and Economic Impact Study}. 
  \bibitem{southeast2023} Southeast Conference. (2023).  \textit{Juneau Tourism Survey 2023}. 
  \bibitem{juneau2016} City and Borough of Juneau. (2016).  \textit{Juneau’s Visitor Industry: Positive Economic Benefits for Our Community}. 
  \bibitem{jedc2024} Juneau Economic Development Council (JEDC). (2024).  \textit{Juneau SEAK Economic Indicators and Outlook Report}. 
  \bibitem{juneau2021} City and Borough of Juneau. (2021).  \textit{Juneau Tourism Survey 2021}. 
  \bibitem{juneau2022} City and Borough of Juneau. (2022).  \textit{Juneau Tourism Survey 2022}. 
  \bibitem{juneau2023} City and Borough of Juneau. (2023).  \textit{Juneau Tourism Survey 2023}. 
  \bibitem{circulator2024} City and Borough of Juneau. (2024).  \textit{Juneau Visitor Circulator Study: Final Report}. 
  \bibitem{budget2016} City and Borough of Juneau Assembly. (2016).  \textit{Biennial Budget Fiscal Year 2016: Year 2 of the FY15/FY16 Biennial Budget}. 
  \bibitem{budget2018} City and Borough of Juneau. (2018).  \textit{Biennial Budget Adopted Fiscal Year 2018: Year 2 of the FY17/18 Biennial Budget}. 
  \bibitem{budget2020} City and Borough of Juneau. (2020).  \textit{Biennial Budget Adopted Fiscal Year 2020: Year 2 of the FY19/20 Biennial Budget}. 
  \bibitem{budget2022} City and Borough of Juneau. (2022).  \textit{Biennial Budget Adopted Fiscal Year 2022: Year 2 of the FY21/22 Biennial Budget}. 
  \bibitem{budget2024} City and Borough of Juneau. (2024).  \textit{Biennial Budget Adopted Fiscal Year 2024: Year 2 of the FY23/24 Biennial Budget}. 
  \bibitem{alaskaInventory}Alaska Department of Environmental Conservation Division of Air Quality. (2023). \textit{Alaska Greenhouse Gas Emissions Inventory}.
  \bibitem{} Alaska Municipal League (2024). \textit{State of Alaska Priority Sustainable Energy Action Plan}
  \bibitem{} UK NIR (2008). \textit{Detailed discussion of methodology and data for estimating $\mathrm{CO}_2$ emissions from fossil fuel combustion}
  \bibitem{} Final Alaska Greenhouse Gas Inventory and Reference
  Case Projections (2009). \textit{Greenhouse Gas Emissions Inventory and Reference Case Projections}
\end{thebibliography}
